### 2023-10-29 conclusions/conclusion.tex
Possibly finished conc

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    \rowcolor{gray}
    Serial size & $n_s=1$ & $n_s=2$ & $n_s=4$ & $n_s=8$\\
    \hline
    Start of first output & $9\mu s$ & $17\mu s$ & $33\mu s$ & $65\mu s$\\
    \hline
    End of first output & $13\mu s$ & $21\mu s$ & $37\mu s$ & $69\mu s$\\
    \hline
    Output period & $9\mu s$ & $17\mu s$ & $33\mu s$ & $65\mu s$\\
    \hline
    Start of last output & $9ms$ & $17ms$ & $33ms$ & $65ms$\\
    \hline
    End of last output & $9ms +4\mu s$ & $17ms+4\mu s$ & $33ms+4\mu s$ & $65ms+4\mu s$\\
    \hline
  \end{tabular}
  \caption{First read values for the different serial sizes}
  \label{tab:readTimesCelegans}
\end{table}

\Cref{tab:readTimesCelegans} shows the output time ranges with thier period.

>>>>

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    \rowcolor{gray}
    Serial size & $n_s=1$ & $n_s=2$ & $n_s=4$ & $n_s=8$\\
    \hline
    Start of first output & $9\mu s$ & $17\mu s$ & $33\mu s$ & $65\mu s$\\
    \hline
    End of first output & $13\mu s$ & $21\mu s$ & $37\mu s$ & $69\mu s$\\
    \hline
    Output period & $9\mu s$ & $17\mu s$ & $33\mu s$ & $65\mu s$\\
    \hline
    Start of last output & $9ms$ & $17ms$ & $33ms$ & $65ms$\\
    \hline
    End of last output & $9ms +4\mu s$ & $17ms+4\mu s$ & $33ms+4\mu s$ & $65ms+4\mu s$\\
    \hline
  \end{tabular}
  \caption{First and last read times for the different serial sizes}
  \label{tab:readTimesCelegans}
\end{table}

\Cref{tab:readTimesCelegans} shows the first and last output time range with the period. All of the output times can be determined using the first time range and using the period. A sequence consists of $500ms$ as explained in \cref{subsec:celegans}, the time steps are physically $500\mu s$ appart, in the case where the circuit would be used to do real time inference, the circuit would have to be slowed down to be on sync with the inputs. The circuit could could be used in a real time use for this time sensitive problem.
